Lattice model

### 2017-03-30 oopsla17/lattice-model.tex
Add exact set and related definitions

  Set of all such intervals (sets) is $\textit{Interval}$.
\end{defn}

@@

@@

\begin{defn}{(Extended origin)}
  In the $N$ dimensional region space, ${(\interv{-1}{1}{\textsf{true}})}^N$ is
  said to be the extended origin.
\end{defn}

\begin{defn}{(Hearing)}
  A point, $p$, in \region{N} is said to \emph{talk to} the extended origin if
%
  \begin{enumerate}
    \item $p$ is in the extended origin;
    \item there are distinct indices $i$ and $j$ (between $1$ and $N$) such that
      $p_i$ is $-1$ to $1$ and there is a $p'$ that talks to the extended origin
      such that $p_j$ is ${p'}_j - 1$ or ${p'}_j + 1$ and for all other indices
      $k$, $p_k$ is ${p'}_k$;
    \item all immediate neighbours of $p$ that are no farther away from the
      extended origin than $p$ can talk to the extended origin.
  \end{enumerate}

  A set of points talk to the extended origin if all points in the set talk to
  the extended origin.
\end{defn}

\begin{lem}
  The following three statements are equivalent for a set of points $P \subseteq
  \mathbb{Z}^N$:
%
  \begin{enumerate}
    \item $P$ defines a superposition of hyper-rectangles each of which crosses
      the extended origin;
    \item $P$ talks to the extended origin
    \item $P$ when regarded as offsets from induction variables forms a
      neighbourhood stencil;
    \item $P$ lies in \region{N}.
  \end{enumerate}
\end{lem}

>>>>

  Set of all such intervals (sets) is $\textit{Interval}$. If the superscript is
  leftout it is treated as \textsf{true}.
\end{defn}

@@

\begin{defn}{(\emph{Point offsets vector})}
  A \emph{point offsets vector}, \textit{poff}, is a an offsets vector such that
  for all indices $i$ $\pi_i(\textit{poff})$, we either have a singleton set or
  the infinite interval $\interv{-\infty}{\infty}{\textsf{true}}$.
\end{defn}

@@

\begin{defn}{(Extended origin)}
  In the $N$ dimensional region space, ${(\interv{-1}{1}{})}^N$ is said to be
  the extended origin denoted $\textit{EO}_N$.
\end{defn}

\begin{defn}{(Origin distance)}
  We measure the \emph{origin distance} of a point offsets vector from the
  extended origin as the minimum number of translations by $\pm 1$ unit in one
  dimension at a time to reach any point in the extended origin. Since point
  offsets vector may represent infinite number of points, we measure the
  distance from the closest one.
\end{defn}
%
\begin{prop}{}
  The closed form of origin distance of an $N$ dimensional point offsets vector
  $p$ is the following:
%
  \begin{align*}
    \textit{dist}_i(p) & = \begin{cases}
      0 & \pi_i(p) = \interv{-\infty}{\infty}{} \\
      |\mathsf{a}| - 1 & \pi_i(p) = \{\mathsf{a}\} \\
    \end{cases} &
%
    |p| & = \sum_{i=1}^{N} dist_i(p)
  \end{align*}
\end{prop}
%
\begin{proof}
\end{proof}

\begin{defn}{(Close neighbourhood)}
  A point offsets vector $p'$ is said to be a close neighbour of point offsets
  vector $p$ if for every index $i$ except $j$, $\pi_i(p)$ agrees with
  $\pi_i(p')$ but at $j$, $\pi_j(p')$ is such that $|p'| + 1 = |p|$.

  This necessarily means point vectors within the extended origin and the
  degenerate point offsets vector with \interv{-\infty}{\infty}{} does not have
  close neighbours.
\end{defn}
%
\begin{prop}
  The unique close neighbour at index $i$ of an $N$ dimensional point offsets
  vector, if it exists, is given by the following partial function:
%
  \begin{align*}
    \mathit{close\_neighbour}(p,i) & = \prod^{N}_{j=1} \mathit{shift}(p,i,j) &
%
    \mathit{shift}(p,i,j) & =
      \begin{cases}
        \{a - 1\} & i = j \wedge \pi_i(p) = \{\mathsf{a}\} \wedge \mathsf{a} > 0\\
        \{a + 1\} & i = j \wedge \pi_i(p) = \{\mathsf{a}\} \wedge \mathsf{a} < 0\\
        \pi_j(p)  & otherwise
      \end{cases}
  \end{align*}
\end{prop}
%
\begin{proof}
\end{proof}

\begin{defn}{(Exact set)}
  The \emph{exact set} at origin distance $d$, $\mathit{ES}_{P,d}$, of a group
  of $N$ dimensional points $P$ is defined below:
%
  \begin{equation*}
    \mathit{ES}_{P,d} =
      \{ p \in P \mid \forall i.\
         p_i \notin \{-1,0,1\} \implies
         \exists p' \in \mathit{ES}_{P,d-1}.\ p' =
         \mathit{close\_neighbour}(p,i) \}
  \end{equation*}
%
  The overall \emph{exact set}, $\mathit{ES}_P$ is then $\mathit{ES}_{P,n}$ such
  tat $\mathit{ES}_{P,n} = \mathit{ES}_{P,n+1}$.
\end{defn}

\begin{lem}
  The following three statements are equivalent for a set of points $P \subseteq
  \mathbb{Z}^N$:
%
  \begin{enumerate}
    \item $P$ defines a superposition of hyper-rectangles each of which crosses
      the extended origin;
    \item $P$ is the same as its exact set $\mathit{ES}_P$;
    \item $P$ when regarded as offsets from induction variables forms a
      neighbourhood stencil;
    \item $P$ is a subset of \region{N}.
  \end{enumerate}
\end{lem}
